\speculake: Hiding Malware in Speculative Execution

### 2018-07-30 paper/related-work.tex
pass on red-pills

% Hardware bare-metal analysis
To combat this Kirat~\textit{et al.} propose automated ``bare-metal''
emulation of malware~\cite{kirat2011barebox}, and methods to determine if malware
is performing red-pill checks to avoid emulation environments~\cite{kirat2014barecloud}.
Symbolic execution can also be used to combat red-pills by finding environmental triggers 
in malicious binaries~\cite{schwartz2010all}.

Unlike other red-pills based on hardware bugs, \speculake cannot be bypassed
by patching binaries as the speculation will only occur on bare-metal systems, 
and the critical functionality is performed speculatively. Similarly, debugging 
break-points will not be triggered as instructions are never completed in a committed state.
Symbolic execution will also fail to find the speculative gadgets as it is never on the
execution pathway.

>>>>

% Hardware bare-metal analysis

``Bare-metal'' emulation of malware~\cite{kirat2011barebox}, methods to
determine if malware is performing red-pill checks to avoid emulation
environments~\cite{kirat2014barecloud}, and symbolic execution can also be used
to combat red-pills by finding environmental triggers in malicious
binaries~\cite{schwartz2010all}.

Unlike other red-pills, \speculake confounds analysts and red-pill detectors
with the use a trigger program and speculative execution. The use of a separate
and benign trigger program controlled by the adversary enables the \speculake
malware to limit detection capabilities. Additionally, as \speculake is executed
via speculative execution, the instructions executed and speculative state are 
also obscured from analysts.

Similarly, debugging break-points will not enable analysts to debug \speculake
malware as break-points interrupt the control flow of a program and prevent
speculative execution. Symbolic execution will also fail to find the speculative
gadgets as it is never on the execution pathway. This allows \speculake to
effectively act as a red-pill while avoiding detection as such.
